\plaintitle

### 2017-06-07 papers/IoT2017/intro.tex

On one hand, transactive energy is a decentralized power system controls problem \cite{7452738}, requiring strategic microgrid control to maintain the stability of the community and the utility. On the other hand, it is a distributed market problem where erroneous as well as malicious transactions can create a gap between demand and supply, eventually destabilizing the system. \Abhishek{We need to bring out the IoT aspect here a bit.} However, in both cases, this system requires a distributed  infrastructure comprising of smart meters, feeders, smart inverters, utility substations, the utility central offices, and the transmission system operator, which has to provide the necessary computation fabric to support the interplay between the energy control and the fiscal market challenges. For example, the Resilient Information Architecture Platform for Smart Grid (RIAPS) \cite{eisele2017riaps} is a distributed IoT  `operating system' that provides the foundations for all algorithms, isolates the hardware details from the algorithms, and provides essential mechanisms for resource management, fault tolerance, and security. \cite{Scott2017ICCPS} also describes a simple transactive energy application using the RIAPS platform.
However, it does not provide the key supports required to handle the privacy challenges that arise from the required information exchange in this decentralized transactive system.

@@

\Abhishek{Can we merge this with last paragraph? It seems repetitive.}
\Aron{I'll probably just remove this.}
Specifically, 
in order to take advantage of local energy production and storage capabilities, 
%in order to take advantage of these capabilities, 
electric grids need to become more decentralized.
However, a decentralized transactive energy system may pose a much greater threat to prosumers' privacy than existing smart metering systems.
\Abhishek{We can introduce these bullets by stating that the privacy challenges specifically are (the privacy challenges were mentioned at the end of the paragraph above.)}
\begin{itemize}
\item Firstly, since prosumers\footnote{We refer to customers as \emph{prosumers} to emphasize that they can not only consume energy, but may also produce it.}  may purchase energy from each other in a transactive microgrid, transactions may inadvertently reveal the prosumers' detailed energy usage patterns to other prosumers within the microgrid.
Addressing this issue in a decentralized trading system is quite challenging as it requires hiding the identities of trade partners from each other.
In comparison, secure smart metering reveals the prosumers' energy usage patterns \Abhishek{Earlier we mentioned the challenge of privacy with respect to system operator in the abstract. I think the system operator and provider are the same.  My question and comment were included in the abstract about this.} only to the provider. 
\item Secondly, \Abhishek{Is this not related to the first point? Perhaps the first point can be just about identity and second point can be specifically about consumption patterns.}\Aron{The first point is about to whom information might be leaked, and the second point is about the type of information. I'll make this more clear.} transactions may reveal the future energy usage of a prosumer, which could be used to infer private information.
For example, a smart home may know that its inhabitants will go out in the evening (e.g., by looking at their calendar), and it may trade energy futures accordingly in the morning.
Without adequate privacy measures, these trades may reveal to other prosumers in the microgrid that the inhabitants will not be at home later.
Note that energy futures, whose delivery may happen several hours after when the transaction is made, can play a very important role in predicting and controlling microgrid load.
In comparison, smart metering reveals only current (and past) usage.
\item Thirdly, transactions and energy usage data in a transactive microgrid are much richer source of information than the simple energy usage data collected by smart meters.
More specifically, the information available in a transactive microgrid is a superset of what is available from smart metering, and it may be used to infer personal information, such as risk propensity and financial standing.
\end{itemize}

>>>>

On one hand, transactive energy is a decentralized power system controls problem \cite{7452738}, requiring strategic microgrid control to maintain the stability of the community and the utility. On the other hand, it is a distributed market problem where erroneous as well as malicious transactions can create a gap between demand and supply, eventually destabilizing the system. However, in both cases, this system requires a distributed  infrastructure comprising of smart meters, feeders, smart inverters, utility substations, the utility central offices, and the transmission system operator, which has to provide the necessary computation fabric to support the interplay between the energy control and the fiscal market challenges. With the advent of IoT-based solutions in smart grid  dynamic demand response systems, which are a precursor to transactive sytems have been made possible \cite{Haider2016166}.

In general the focus is now on creating a distributed  IoT infrastructure comprising of smart meters, feeders, smart inverters, utility substations, the utility central offices, and the transmission system operator, which has to provide the necessary computation fabric to support the interplay between the energy control and the fiscal market challenges, as shown by Volttron \cite{katipamula2016volttron},  OpenFMB \cite{gunthersmart}, and the Resilient Information Architecture Platform for Smart Grid (RIAPS) \cite{eisele2017riaps}\cite{Scott2017ICCPS}, which is a distributed IoT  `operating system' that provides the foundations for all algorithms, isolates the hardware details from the algorithms, and provides essential mechanisms for resource management, fault tolerance, and security. However, most of these efforts are focusing on the computation and distribution of information and do not provide the key supports required to handle the privacy challenges that arise from the required information exchange in this decentralized transactive system.

In this paper, we assume the existence of the IoT infrastructure and specifically focus on the privacy challenges mentined below.

@@

%\Abhishek{Can we merge this with last paragraph? It seems repetitive.}
%\Aron{I'll probably just remove this.}
%Specifically, 
%in order to take advantage of local energy production and storage capabilities, 
%in order to take advantage of these capabilities, 
%electric grids need to become more decentralized.
%However, a decentralized transactive energy system may pose a much greater threat to prosumers' privacy than existing smart metering systems.
%\Abhishek{We can introduce these bullets by stating that the privacy challenges specifically are (the privacy challenges were mentioned at the end of the paragraph above.)}
\begin{itemize}
\item Firstly, since prosumers\footnote{We refer to customers as \emph{prosumers} to emphasize that they can not only consume energy, but may also produce it.}  may purchase energy from each other in a transactive microgrid, transactions may inadvertently reveal the prosumers' detailed energy usage patterns to other prosumers within the microgrid.
Addressing this issue in a decentralized trading system is quite challenging as it requires hiding the identities of trade partners from each other.
In comparison, secure smart metering reveals the prosumers' energy usage patterns \Abhishek{Earlier we mentioned the challenge of privacy with respect to system operator in the abstract. I think the system operator and provider are the same.  My question and comment were included in the abstract about this.} only to the provider. 
\item Secondly, \Abhishek{Is this not related to the first point? Perhaps the first point can be just about identity and second point can be specifically about consumption patterns.}\Aron{The first point is about to whom information might be leaked, and the second point is about the type of information. I'll make this more clear.} transactions may reveal the future energy usage of a prosumer, which could be used to infer private information.
For example, a smart home may know that its inhabitants will go out in the evening (e.g., by looking at their calendar), and it may trade energy futures accordingly in the morning.
Without adequate privacy measures, these trades may reveal to other prosumers in the microgrid that the inhabitants will not be at home later.
Note that energy futures, whose delivery may happen several hours after when the transaction is made, can play a very important role in predicting and controlling microgrid load.
In comparison, smart metering reveals only current (and past) usage.
\item Thirdly, transactions and energy usage data in a transactive microgrid are much richer source of information than the simple energy usage data collected by smart meters.
More specifically, the information available in a transactive microgrid is a superset of what is available from smart metering, and it may be used to infer personal information, such as risk propensity and financial standing.
\end{itemize}
